Automated Topic Naming

### 2012-01-19 ese/ese.tex
finished migod's comments\nremoved a redundant section on IRR

\subsection{Summary of Techniques}
While an unsupervised technique such as LDA is appealing in its lack of human intervention, and thus lower effort, 
supervised learners have the advantage of domain knowledge, which typically means improved results. 
% NEIL - we got criticized for making it sound like this is the obvious thing to do... and then why do you need a learner?
%Our manual annotations were fairly quick to do, taking only a few minutes per 30 day period. 
Creating annotated topics (i.e., manual labels) for training is painstaking, but with a suitably representative set of topics, the effort is acceptable. To
annotate \emph{all} topics took us approximately 20 hours per project, but we estimate only 10\% of the topics need annotation to produce useful results.

@@

We found that the multi-label learners of BR, CLR and HOMER only did
as well or worse for Macro-ROC as the single-label Naive Bayes and other naive Bayes-derived learners. 
This suggests that by combining together multiple Naive Bayes learners
we could probably label sets of topics effectively, but it would
require a separate Naive Bayes learner per label.

@@

Our work faced multiple threats to validity and we attempted to address many of them:

\emph{Construct validity} -- we used only commit messages rather than
mail or bug tracker messages. 
To extend further we would need matching repositories for each project.
%Each case study was BecauseSince we required a seamless record, it was not possible to obtain
%other data sources. 
Possibly they would have influenced our results, but there would be a degree of correlation between the corpora.
 It is possible for a given label to occur across the arbitrary 30-day boundary we set. We suspect but have not proved that this is insignificant. 
%Conversely, construct validity was addressed in our validation as we used the files, topics and revisions to annotate the commit messages. 
%We used mailing-lists to verify the purpose behind some events.
Our taxonomy for software NFRs is subject to dispute, but seems to be
generally accepted.  A future approach should consider a different taxonomy, such as one created by surveying developers on what ``types" of tasks they work on.
Finally, there are exogenous sources, such as
in-person discussions, which we did not access.  %We did not show these results to the stakeholders.

@@

Developer style is another confounding issue, if we are searching for
these words we are relying on developers to use these words. This
study might be exploiting the behaviour or style of a few
developers. If one developer did not describe their commits well or
used fewer terms it is likely they would be associated with a NFR
topic regardless of the actual purpose of their commits.

\emph{Internal validity} -- %includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model.

@@

%XXX If we have more time try to elaborate more on this
One potential issue with some of our results is that we achieved very
low ROC and F-Measure scores.  Performance was not uniformly low,
often the more common classes exhibited better performance than the
more rare classes.  Often this was amplified by class imbalance. In
future work we plan to investigate techniques such as sub-sampling and
boot-strapping in order to improve performance. Some of the ROC
performance could be due to a lack of coherence in tagging which was
shown by our low inter-rater reliability score.

We assessed inter-rater reliability (IRR), a measure of the correlation between the manual annotations the first two authors created. Perfect IRR (1.0) indicates complete agreement 
on the appropriate annotation for that topic. We verified IRR using
manually annotated PostgreSQL topics, and achieved a weak result of $0.1$.
Some of the reasons for this are a disagreement over the appropriate classification for documentation topics (should this be considered
usability or portability?). A short education session on what a given
NFR from the ISO standard encompasses would reduce this error rate.
Weak IRR results could also be responsible for some the low ROC
performance, if each rater is picking up on different information it
might make it more difficult to train a machine learner to do the
same.
Furthermore weak IRR results threatens the validity of the
experiments, if raters cannot agree then consistently labelling by
ISO-9126 related NFRs could be quite difficult.

\emph{External validity} -- %was addressed by our use of two case studies, but there are still issues. 
Our data originated from OSS database projects and thus might not be applicable to commercially developed software or other domains. 
Furthermore, our analysis techniques rely on a project's use of meaningful commit messages, although we feel this is the most frequently occurring form
of developer comments. 
While we tried to control for application domain variability, OSS
projects investigated were database systems, thus our results might
not generalize well to other domains.

% in Case Study Research: Design Case Studies
\emph{Reliability} -- each annotator, the first two authors, followed the same protocol and used the same annotations. 
However, only two annotators were used; their annotations exhibit some
bias as suggested by the weak inter-rater reliability for
PostgreSQL. Inter-rater reliability could not be checked for MySQL and
MaxDB because annotators did not rate the same documents.

>>>>

\subsection{Summary of Techniques}
While an unsupervised technique such as LDA is appealing in its lack of human intervention, and thus lower effort, 
supervised learners have the advantage of domain knowledge, which typically means improved results. 
% NEIL - we got criticized for making it sound like this is the obvious thing to do... and then why do you need a learner?
%Our manual annotations were fairly quick to do, taking only a few minutes per 30 day period. 
Creating annotated topics (i.e., manual labels) for training is painstaking, but with a suitably representative set of topics, we feel that the effort is acceptable for non-academic use. To
annotate \emph{all} topics took us approximately 20 hours per project, but we estimate only 10\% of the topics need annotation to produce useful results.

@@

We found that the multi-label learners of BR, CLR and HOMER performed only 
as well or worse for Macro-ROC as the single-label Naive Bayes and other naive Bayes-derived learners. 
This suggests that by combining together multiple Naive Bayes learners
we could probably label sets of topics effectively, but it would
require a separate Naive Bayes learner per label.

@@

Our work faced multiple threats to validity and we have attempted to address them:

\paragraph{Construct validity} -- we used only commit messages rather than
mail or bug tracker messages. 
To extend further we would need matching repositories for each project.
%Each case study was BecauseSince we required a seamless record, it was not possible to obtain
%other data sources. 
Possibly they would have influenced our results, but there would be a degree of correlation between the corpora.
 It is possible for a given label to occur across the arbitrary 30-day boundary we set. We suspect but have not proved that this is insignificant. 
%Conversely, construct validity was addressed in our validation as we used the files, topics and revisions to annotate the commit messages. 
%We used mailing-lists to verify the purpose behind some events.
Our taxonomy for software NFRs is subject to dispute, but seems to be
generally accepted.  A future approach should consider a different taxonomy, such as one created by surveying developers on what ``types" of tasks they work on.
Finally, there are exogenous sources, such as
in-person discussions, which we did not access.  %We did not show these results to the stakeholders.

@@

Developer style is another confounding issue; if we are searching for
words in a word-list, we are relying on developers to use these words. This
study might be exploiting the behaviour or style of a few
developers. If one developer did not describe their commits well or
used fewer terms it is likely they would be associated with a NFR
topic regardless of the actual purpose of their commits.

\paragraph{Internal validity} -- %includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model.

@@

%XXX If we have more time try to elaborate more on this
One potential issue with some of our results is that we achieved very
low ROC and F-Measure scores.  Performance was not uniformly low,
as the more common classes often exhibited better performance than the
more rare classes.  Often this was amplified by class imbalance. In
future work we plan to investigate techniques such as sub-sampling and
boot-strapping in order to improve performance. Some of the ROC
performance could be due to a lack of coherence in tagging which was
shown by our low inter-rater reliability score. Inter-rater reliability is a threat, and we discussed it in Section \ref{sec:inter-rater}. 
% We assessed inter-rater reliability (IRR), a measure of the correlation between the manual annotations the first two authors created. Perfect IRR (1.0) indicates complete agreement 
% on the appropriate annotation for that topic. We verified IRR using
% manually annotated PostgreSQL topics, and achieved a weak result of $0.1$.
% Some of the reasons for this are a disagreement over the appropriate classification for documentation topics (should this be considered
% usability or portability?). A short education session on what a given
% NFR from the ISO standard encompasses would reduce this error rate.
% Weak IRR results could also be responsible for some the low ROC
% performance, if each rater is picking up on different information it
% might make it more difficult to train a machine learner to do the
% same.
% Furthermore weak IRR results threatens the validity of the
% experiments, if raters cannot agree then consistently labelling by
% ISO-9126 related NFRs could be quite difficult.

\paragraph{External validity} -- %was addressed by our use of two case studies, but there are still issues. 
Our data originated from OSS database projects and thus might not be applicable to commercially developed software or other domains. 
Furthermore, our analysis techniques rely on a project's use of meaningful commit messages, although we feel this is the most frequently occurring form
of developer comments. 
While we tried to control for application domain variability, OSS
projects investigated were database systems, thus our results might
not generalize well to other domains.

% in Case Study Research: Design Case Studies
\paragraph{Reliability} -- each annotator, the first two authors, followed the same protocol and used the same annotations. 
However, only two annotators were used; their annotations exhibit some
bias as suggested by the weak inter-rater reliability for
PostgreSQL. Inter-rater reliability could not be checked for MySQL and
MaxDB because annotators did not rate the same documents. This is discussed at length in Section \ref{sec:inter-rater}
